The universal property of infinite direct sums in C$^*$-categories and W$^*$-categories

### 2019-06-28 direct_sums.tex
recap of operator algs

@@

\begin{comment} % T: I'm not sure if the following would be helpful, given that we assume familiarity with C*- and W*-algebras
As the definitions of~C$^*$- and~W$^*$-categories
    will implicitly define~C$^*$- and W$^*$-algebras,
    we only comment briefly on the latter.
Every subalgebra of the algebra of complex~$n\times n$-matrices
    is a C$^*$- and~W$^*$-algebra.
More generally, every norm closed and $*$-closed subalgebra of~$\B{\H}$,
    the bounded operators on a Hilbert space~$\H$,
    is a C$^*$-algebra and, in fact,
    every C$^*$-algebra is isomorphic to such a subalgebra
        of~$\B{\H}$ for some Hilbert space~$\H$.
Every weakly closed subalgebra of~$\B{\H}$ is a W$^*$-algebra,
    and every W$^*$-algebra is isomorphic to such a weakly closed subalgebra.
Moreover, every commutative unital C$^*$-algebra is isomorphic to~$C(X)$ for some
    compact Hausdorff space~$X$, 
        and every commutative W$^*$-algebra is isomorphic to~$L^\infty(X,\mu)$ for some
            complete finite measure space~$(X,\mu)$.
\end{comment}

@@

% vim: ft=tex.latex

>>>>

\subsection*{C*-algebras and W*-algebras}  We give a very brief recap of C*-algebras and W*-algebras for the benefit of readers who have a background in category theory but not in operator algebras, while referring to the literature for the details~\cite{sakai}.

\emph{C$^*$-algebras} are abstract versions of algebras of operators on a Hilbert space which are closed in the operator norm and closed under taking adjoint operators, where taking adjoints is encoded in the ``star'' operation $*$. Similarly, \emph{W$^*$-algebras} are abstract versions of algebras of operators on a Hilbert space which are in addition closed under limits with respect to pointwise convergence (strong operator topology). In fact, every abstract C$^*$-algebra or W$^*$-algebra is isomorphic to one having such a concrete representation. For example, every $*$-closed subalgebra of the algebra of complex~$n\times n$-matrices is a C$^*$-algebra and a~W$^*$-algebra. Moreover, every commutative unital C$^*$-algebra is isomorphic to~$C(X)$ for some compact Hausdorff space~$X$. And every commutative W$^*$-algebra is isomorphic to~$L^\infty(X,\mu)$ for some complete finite measure space~$(X,\mu)$.

@@

@@

 vim: ft=tex.latex
